---
title: "Exploration and Visualization"
author: "Yixi Xu"
output: 
  html_document:
    code_folding: hide
    toc: true
    toc_float: true
---

```{r include=FALSE, warning=FALSE}
library(dplyr)
library(tidyverse)
library(httr)
library(rvest)
library(stringr)
library(forcats)
library(viridis)
library(readr)
library(tidytext)
library(rvest)
library(janitor)
library(haven)
library(DT)
library(plotly)
```

```{r data_prepare, warning=FALSE}
# read IMDB data from Kaggle
movie_with_boxoffice = read.csv("./data/IMDB-Movie-Data_new.csv")
```


##Top ranked movies with best box-office 

```{r warning=FALSE, message=FALSE}
##Top ranked movies with best box-office 
movie_with_boxoffice %>% 
  group_by(movie_title) %>% 
  summarize(box_movie = sum(total_gross_millions, na.rm = TRUE)) %>% 
  arrange(desc(box_movie)) %>% 
  datatable(class = 'cell-border stripe')

movie_with_boxoffice %>% 
  group_by(movie_title) %>%
  summarize(box_movie = sum(total_gross_millions,na.rm = TRUE)) %>% 
  top_n(10) %>% 
  arrange(desc(box_movie)) %>% 
  mutate(move_title = fct_reorder(movie_title, box_movie)) %>% 
  plot_ly(x = ~movie_title,  y = ~box_movie, color = ~movie_title, type = "bar") %>% 
   layout(title = 'Total Movie Box Office For Each Movie',
         xaxis = list(title =""),
         yaxis = list(title ="total movie box office"),
         margin = list(b = 160))
```

##Top ranked movies with best review_score

```{r warning=FALSE}
##Top ranked movies with best review_score
movie_with_boxoffice %>% 
  group_by(movie_title) %>% 
  select(movie_title, review_score) %>% 
  arrange(desc(review_score)) %>% 
  datatable(class = 'cell-border stripe')
```

##Top ranked movies with best rating

```{r warning=FALSE}
##Top ranked movies with best rating
movie_with_boxoffice %>% 
  group_by(movie_title) %>% 
  select(movie_title, rating) %>% 
  arrange(desc(rating)) %>% 
  datatable(class = 'cell-border stripe')
```

##Top ranked movies with highest votes 

```{r warning=FALSE}
##Top ranked movies with highest votes 
movie_with_boxoffice %>% 
  group_by(movie_title) %>% 
  select(movie_title, votes) %>% 
  arrange(desc(votes)) %>% 
  datatable(class = 'cell-border stripe')
```

##Top ranked movies with longest runtime 

```{r warning=FALSE}
##Top ranked movies with longest runtime 
movie_with_boxoffice %>% 
  group_by(movie_title) %>% 
  select(movie_title, runtime_minutes) %>% 
  arrange(desc(runtime_minutes)) %>% 
  datatable(class = 'cell-border stripe')
```



##Director:  The top ranked director with best box-office

```{r warning=FALSE, message=FALSE}
##Director:  The top ranked director with best box-office
movie_with_boxoffice %>% 
  group_by(director) %>% 
  summarize(box_movie = sum(total_gross_millions, na.rm = TRUE), mean_review = mean(review_score, na.rm = TRUE)) %>% 
  arrange(desc(box_movie)) %>% 
  datatable(class = 'cell-border stripe')

movie_with_boxoffice %>% 
  group_by(director) %>% 
  summarize(box_movie = sum(total_gross_millions, na.rm = TRUE)) %>% 
  top_n(10) %>% 
  mutate(director = fct_reorder(director, box_movie)) %>% 
  plot_ly(., x = ~director,  y = ~box_movie, color = ~factor(director), type = "bar") %>%
   layout(title = ' The top 10 director with best box-office',
         xaxis = list(title =""),
         yaxis = list(title ="total movie box office"),
         margin = list(b = 160))
```

##Genre of movie
###Distribution of movie genre

```{r warning=FALSE}
## Distribution of movie genre 
##Donut charts represent genre 
movie_with_boxoffice %>% 
  mutate(genre = as.character(genre)) %>% 
  unnest_tokens(word, genre) %>% 
  mutate(genre = word) %>% 
  group_by(genre) %>%
  summarize(n = n()) %>% 
  filter(!genre=="fi") %>% 
  mutate(genre = stringr::str_replace(genre, "sci", "sci-fi")) %>% 
  arrange(desc(n)) %>% 
  plot_ly(labels = ~genre, values = ~n, textposition = 'inside',
        textinfo = 'label+percent') %>%
  add_pie(hole = 0.6) %>%
  layout(title = "Distribution of different movie genre type",  showlegend = FALSE,
         xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
         yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE)) 
```


###The top ranked type of movies with best box-office

```{r warning=FALSE}
##Type: The top ranked type of movies with best box-office
movie_with_boxoffice %>% 
  mutate(genre = as.character(genre)) %>% 
  unnest_tokens(word,genre) %>% 
  mutate(genre = word) %>% 
  group_by(genre)%>%
  summarize(box_movie = sum(total_gross_millions, na.rm = TRUE), mean_review = mean(review_score, na.rm = TRUE)) %>% 
  filter(!genre=="fi") %>% 
  mutate(genre = stringr::str_replace(genre, "sci", "sci-fi")) %>%
  arrange(desc(box_movie)) %>% 
  datatable(class = 'cell-border stripe')

movie_with_boxoffice %>% 
  mutate(genre = as.character(genre)) %>% 
  tidytext::unnest_tokens(word, genre) %>% 
  mutate(genre = word) %>% 
  group_by(genre) %>%
  summarize(box_movie = sum(total_gross_millions, na.rm = TRUE)) %>% 
  filter(!genre=="fi") %>% 
  mutate(genre = stringr::str_replace(genre, "sci", "sci-fi")) %>% 
  mutate(genre = fct_reorder(genre, box_movie)) %>% 
  plot_ly(., x = ~genre,  y = ~box_movie, color = ~genre, type = "bar") %>% 
   layout(title = 'Total Movie Box Office For Each Movie Type',
         xaxis = list(title =""),
         yaxis = list(title ="total movie box office"),
         margin = list(b = 160))
```

**Comment**: From two plots and datatable above, we found out that,during 2006 to 2016, drama movie is the most common movie type, and adventure movie has the best total movie box, histroy moive has the best mean review score. 

###Actor/Actress:  The top ranked actor/actress with best box-office

```{r warning=FALSE, message=FALSE}
##Actor/Actress:  The top ranked actor/actress with best box-office
movie_with_boxoffice %>% 
  gather(key = actor, value = main_actor, actor1:actor4) %>% 
  group_by(main_actor) %>%
  summarize(box_movie = sum(total_gross_millions, na.rm = TRUE)) %>% 
  arrange(desc(box_movie)) %>% 
  datatable(class = 'cell-border stripe')

movie_with_boxoffice %>% 
  gather(key = actor, value = main_actor, actor1:actor4) %>% 
  group_by(main_actor) %>% 
  summarize(box_movie = sum(total_gross_millions,na.rm = TRUE)) %>% 
  top_n(10) %>% 
  mutate(main_actor = fct_reorder(main_actor, box_movie)) %>% 
  plot_ly(., x = ~main_actor,  y = ~box_movie, color = ~main_actor, type = "bar") %>%
   layout(title = ' The top 10 actor/actress with best box-office',
         xaxis = list(title =""),
         yaxis = list(title ="total movie box office"),
         margin = list(b = 160))
```


##Production company:  The top ranked production company  with best box-office

```{r warning=FALSE}
##Production company:  The top ranked production company  with best box-office
movie_with_boxoffice %>% 
  group_by(studio) %>%
  na.omit() %>% 
  summarize(box_movie = sum(total_gross_millions,na.rm = TRUE)) %>% 
  arrange(desc(box_movie)) %>% 
  datatable(class = 'cell-border stripe')

movie_with_boxoffice %>% 
  group_by(studio) %>%
  na.omit() %>% 
  summarize(box_movie = sum(total_gross_millions,na.rm = TRUE)) %>% 
  mutate(studio = fct_reorder(studio, box_movie)) %>% 
  plot_ly(., x = ~studio,  y = ~box_movie, color = ~studio, type = "bar") %>% 
   layout(title = 'Total Movie Box Office For Each Studio',
         xaxis = list(title =""),
         yaxis = list(title ="total movie box office"),
         margin = list(b = 160))

```


##Word Cloud for Movie Descriptions from 2006 to 2016
```{r echo = FALSE, fig.align='center', warning=FALSE, message=FALSE}
# Install
# install.packages("tm")  # for text mining
# install.packages("SnowballC") # for text stemming
# install.packages("wordcloud") # word-cloud generator 
# install.packages("RColorBrewer") # color palettes
# Load
library("tm")
library("SnowballC")
library("wordcloud")
library("RColorBrewer")
library(tidyverse)

# create text files containing movie names in order to make a word cloud
# movies_names = read_csv("IMDB-Movie-Data.csv") %>% 
#   select(Title) %>% 
#   write.table(., "movies_names.txt", sep="\t")

movie_with_boxoffice %>% 
  select(description) %>% 
  write.table(., "description.txt", sep="\t")

text = as.character(readLines("description.txt"))
docs = tm::Corpus(tm::VectorSource(text))
toSpace <- content_transformer(function (x , pattern ) gsub(pattern, " ", x))
docs <- tm_map(docs, toSpace, "/")
docs <- tm_map(docs, toSpace, "@")
docs <- tm_map(docs, toSpace, "\\|")
# Convert the text to lower case
docs <- tm_map(docs, content_transformer(tolower))
# Remove numbers
docs <- tm_map(docs, removeNumbers)
# Remove english common stopwords
docs <- tm_map(docs, removeWords, stopwords("english"))
# Remove your own stop word
# specify your stopwords as a character vector
docs <- tm_map(docs, removeWords, c("blabla1", "blabla2")) 
# Remove punctuations
docs <- tm_map(docs, removePunctuation)
# Eliminate extra white spaces
docs <- tm_map(docs, stripWhitespace)
# Text stemming
# docs <- tm_map(docs, stemDocument)
dtm <- TermDocumentMatrix(docs)
m <- as.matrix(dtm)
v <- sort(rowSums(m),decreasing=TRUE)
d <- data.frame(word = names(v),freq=v)

set.seed(1)
wordcloud(words = d$word, freq = d$freq, min.freq = 1,
          max.words=200, random.order=FALSE, rot.per=0.35, 
          colors=brewer.pal(8, "Dark2"))
```

**Comment**: According to  word cloud for moive descripition, the most frequent words include young, life, world ,new.