---
title: "final project"
output: html_document
---

```{r results='hide', message=FALSE, warning=FALSE,echo=FALSE}
library(dplyr)
library(tidyverse)
library(httr)
library(rvest)
library(stringr)
library(forcats)
library(viridis)
library(readr)
library(tidytext)
library(rvest)
library(janitor)
library(haven)
library(DT)
library(plotly)
```

```{r data_prepare, include=FALSE,warning=FALSE,echo=FALSE}
# read IMDB data from Kaggle
movie = read.csv("./data/IMDB-Movie-Data.csv")

# read boxoffice data from internet
url_base = "http://www.boxofficemojo.com/yearly/chart/?view=releasedate&view2=domestic&yr="

# create url strings for 2006 - 2016 boxoffice data; only include movies with top 100 total gross in each year. 
urls = str_c(url_base, 2006:2016, "&sort=gross&order=DESC&p=.htm")
output = vector("list", 11)

# create for loop to generate the 2006 - 2016 boxoffice dataframe
boxoffice = NULL
for (i in 1:11) {

output[[i]] = read_html(urls[[i]])

output[[i]] %>% 
html_nodes(css = "table")

box_office_year = (output[[i]] %>% html_nodes(css = "table"))[[7]] %>%
  html_table(fill = TRUE) 
  
colnames(box_office_year) = box_office_year[1,]
colnames(box_office_year)[2] = "movie_title"
colnames(box_office_year)[3] = "studio"
colnames(box_office_year)[4] = "total_gross"
colnames(box_office_year)[5] = "theaters"
colnames(box_office_year)[6] = "opening"
colnames(box_office_year)[7] = "theaters_opening"  

box_office_year = box_office_year %>% 
  select(movie_title, studio, total_gross, opening) %>% 
  .[3:102,] %>%
  mutate(year = 2005 + i)
    
boxoffice = bind_rows(boxoffice, box_office_year)  
}

set.seed(1)
# renmae the movie_title in movie dataset in order to join two datasets
movie_rename= movie %>% 
  clean_names() %>% 
  rename("movie_title" = "title",
         "review_score" = "metascore")

# joining two datasets; tidy data set
movie_with_boxoffice = left_join(movie_rename, boxoffice, by=c("movie_title", "year")) %>% 
  rename("open_gross" = "opening")  

# Replace NA values in total_gross with the revenue column in movie dataset
total_gross_na = is.na(movie_with_boxoffice$total_gross)

movie_with_boxoffice$total_gross[total_gross_na] =  movie_with_boxoffice$revenue_millions[total_gross_na]*10^6

# eliminate $sign and "," of the total gross and open gross, remove rows with review scores is NA:
movie_with_boxoffice = movie_with_boxoffice %>% 
  mutate(total_gross = gsub("\\$", "", total_gross),
         total_gross = gsub(",", "", total_gross),
         total_gross = as.numeric(total_gross),
         open_gross = gsub("\\$", "", open_gross),
         open_gross = gsub(",", "", open_gross),
         open_gross = as.numeric(open_gross)) %>% 
  mutate(total_gross_millions = total_gross / 10^6,
         open_gross_millions = open_gross / 10^6,
         actors_sep = actors,
         genre_sep = genre) %>% 
  select(-total_gross, -revenue_millions, -open_gross) %>% 
  separate(., actors_sep, c("actor1","actor2", "actor3", "actor4"), sep=",") %>% 
  separate(genre_sep, into = c("genre1", "genre2", "genre3"), sep = ",")
```


##Top ranked movies with best box-office 

```{r warning=FALSE,echo=FALSE}
##Top ranked movies with best box-office 
movie_with_boxoffice %>% 
  group_by(movie_title) %>% 
  summarize(box_movie = sum(total_gross_millions, na.rm = TRUE)) %>% 
  arrange(desc(box_movie)) %>% 
  datatable()
```

##Top ranked movies with best review_score

```{r warning=FALSE,echo=FALSE}
##Top ranked movies with best review_score
movie_with_boxoffice %>% 
  group_by(movie_title) %>% 
  select(movie_title, review_score) %>% 
  arrange(desc(review_score)) %>% 
  datatable()
```

##Top ranked movies with best rating

```{r warning=FALSE,echo=FALSE}
##Top ranked movies with best rating
movie_with_boxoffice %>% 
  group_by(movie_title) %>% 
  select(movie_title, rating) %>% 
  arrange(desc(rating)) %>% 
  datatable()
```

##Top ranked movies with highest votes 

```{r warning=FALSE,echo=FALSE}
##Top ranked movies with highest votes 
movie_with_boxoffice %>% 
  group_by(movie_title) %>% 
  select(movie_title, votes) %>% 
  arrange(desc(votes)) %>% 
  datatable()
```

##Top ranked movies with longest runtime 

```{r warning=FALSE,echo=FALSE}
##Top ranked movies with longest runtime 
movie_with_boxoffice %>% 
  group_by(movie_title) %>% 
  select(movie_title, runtime_minutes) %>% 
  arrange(desc(runtime_minutes)) %>% 
  datatable()
```

##Distribution of movie genre

```{r warning=FALSE,echo=FALSE}
## Distribution of movie genre 
##Donut charts represent genre 
movie_with_boxoffice %>% 
  mutate(genre = as.character(genre)) %>% 
  unnest_tokens(word, genre) %>% 
  mutate(genre = word) %>% 
  group_by(genre) %>%
  summarize(n = n()) %>% 
  filter(!genre=="fi") %>% 
  mutate(genre = stringr::str_replace(genre, "sci", "sci-fi")) %>% 
  arrange(desc(n)) %>% 
  plot_ly(labels = ~genre, values = ~n, textposition = 'inside',
        textinfo = 'label+percent') %>%
  add_pie(hole = 0.6) %>%
  layout(title = "Distribution of different movie genre type",  showlegend = FALSE,
         xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
         yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE)) 
```

##Director:  The top ranked director with best box-office

```{r warning=FALSE,echo=FALSE}
##Director:  The top ranked director with best box-office
movie_with_boxoffice %>% 
  group_by(director) %>% 
  summarize(box_movie = sum(total_gross_millions, na.rm = TRUE), mean_review = mean(review_score, na.rm = TRUE)) %>% 
  arrange(desc(box_movie)) %>% 
  datatable()
```

##Type: The top ranked type of movies with best box-office

```{r warning=FALSE,echo=FALSE}
##Type: The top ranked type of movies with best box-office
movie_with_boxoffice %>% 
  mutate(genre = as.character(genre)) %>% 
  unnest_tokens(word,genre) %>% 
  mutate(genre = word) %>% 
  group_by(genre)%>%
  summarize(box_movie = sum(total_gross_millions, na.rm = TRUE), mean_review = mean(review_score, na.rm = TRUE)) %>% 
  filter(!genre=="fi") %>% 
  mutate(genre = stringr::str_replace(genre, "sci", "sci-fi")) %>%
  arrange(desc(box_movie)) %>% 
  datatable()

movie_with_boxoffice %>% 
  mutate(genre = as.character(genre)) %>% 
  tidytext::unnest_tokens(word, genre) %>% 
  mutate(genre = word) %>% 
  group_by(genre) %>%
  summarize(box_movie = sum(total_gross_millions, na.rm = TRUE)) %>% 
  filter(!genre=="fi") %>% 
  mutate(genre = stringr::str_replace(genre, "sci", "sci-fi")) %>% 
  mutate(genre = fct_reorder(genre, box_movie)) %>% 
  plot_ly(., x = ~genre,  y = ~box_movie, color = ~genre, type = "bar") %>% 
   layout(title = 'Total Movie Box Office For Each Movie Type',
         xaxis = list(title =""),
         yaxis = list(title ="total movie box office"))

##range 
```

##Actor/Actress:  The top ranked actor/actress with best box-office

```{r warning=FALSE,echo=FALSE}
##Actor/Actress:  The top ranked actor/actress with best box-office
movie_with_boxoffice %>% 
  gather(key = actor, value = main_actor, actor1:actor4) %>% 
  group_by(main_actor) %>%
  summarize(box_movie = sum(total_gross_millions, na.rm = TRUE)) %>% 
  arrange(desc(box_movie)) %>% 
  datatable()
```

##Production company:  The top ranked production company  with best box-office

```{r warning=FALSE,echo=FALSE}
##Production company:  The top ranked production company  with best box-office
movie_with_boxoffice %>% 
  group_by(studio) %>%
  na.omit() %>% 
  summarize(box_movie = sum(total_gross_millions,na.rm = TRUE)) %>% 
  arrange(desc(box_movie)) %>% 
  datatable()

movie_with_boxoffice %>% 
  group_by(studio) %>%
  na.omit() %>% 
  summarize(box_movie = sum(total_gross_millions,na.rm = TRUE)) %>% 
  mutate(studio = fct_reorder(studio, box_movie)) %>% 
  plot_ly(., x = ~studio,  y = ~box_movie, color = ~studio, type = "bar") %>% 
   layout(title = 'Total Movie Box Office For Each Studio',
         xaxis = list(title =""),
         yaxis = list(title ="total movie box office"))

```

**Word Cloud for Movie Descriptions from 2006 to 2016**
```{r echo = FALSE, fig.align='center', warning=FALSE, message=FALSE,echo=FALSE}
# Install
# install.packages("tm")  # for text mining
# install.packages("SnowballC") # for text stemming
# install.packages("wordcloud") # word-cloud generator 
# install.packages("RColorBrewer") # color palettes
# Load
library("tm")
library("SnowballC")
library("wordcloud")
library("RColorBrewer")
library(tidyverse)

# create text files containing movie names in order to make a word cloud
# movies_names = read_csv("IMDB-Movie-Data.csv") %>% 
#   select(Title) %>% 
#   write.table(., "movies_names.txt", sep="\t")


movie_with_boxoffice %>% 
  select(description) %>% 
  write.table(., "description.txt", sep="\t")


text = as.character(readLines("description.txt"))
docs = tm::Corpus(tm::VectorSource(text))
toSpace <- content_transformer(function (x , pattern ) gsub(pattern, " ", x))
docs <- tm_map(docs, toSpace, "/")
docs <- tm_map(docs, toSpace, "@")
docs <- tm_map(docs, toSpace, "\\|")
# Convert the text to lower case
docs <- tm_map(docs, content_transformer(tolower))
# Remove numbers
docs <- tm_map(docs, removeNumbers)
# Remove english common stopwords
docs <- tm_map(docs, removeWords, stopwords("english"))
# Remove your own stop word
# specify your stopwords as a character vector
docs <- tm_map(docs, removeWords, c("blabla1", "blabla2")) 
# Remove punctuations
docs <- tm_map(docs, removePunctuation)
# Eliminate extra white spaces
docs <- tm_map(docs, stripWhitespace)
# Text stemming
# docs <- tm_map(docs, stemDocument)
dtm <- TermDocumentMatrix(docs)
m <- as.matrix(dtm)
v <- sort(rowSums(m),decreasing=TRUE)
d <- data.frame(word = names(v),freq=v)

set.seed(1)
wordcloud(words = d$word, freq = d$freq, min.freq = 1,
          max.words=200, random.order=FALSE, rot.per=0.35, 
          colors=brewer.pal(8, "Dark2"))
