---
title: "P8105_final_mc4433"
author: "Manqi Cai"
output: 
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r packages, echo=FALSE, warning=FALSE}

library(dplyr)
library(tidyverse)
library(httr)
library(rvest)
library(janitor)
library(stringr)
library(ggplot2)
library(hexbin)
library(plotly)
library(knitr)
library(DT)
library(leaps)
library(stats)
library(MASS)

```

# Prepare datasets
```{r data_prepare, echo=FALSE, warning=FALSE}
# read IMDB data from Kaggle
movie = read.csv("./data/IMDB-Movie-Data.csv")

# read boxoffice data from internet
url_base = "http://www.boxofficemojo.com/yearly/chart/?view=releasedate&view2=domestic&yr="

# create url strings for 2006 - 2016 boxoffice data; only include movies with top 100 total gross in each year. 
urls = str_c(url_base, 2006:2016, "&sort=gross&order=DESC&p=.htm")
output = vector("list", 11)

# create for loop to generate the 2006 - 2016 boxoffice dataframe
boxoffice = NULL
for (i in 1:11) {

output[[i]] = read_html(urls[[i]])

output[[i]] %>% 
html_nodes(css = "table")

box_office_year = (output[[i]] %>% html_nodes(css = "table"))[[7]] %>%
  html_table(fill = TRUE) 
  
colnames(box_office_year) = box_office_year[1,]
colnames(box_office_year)[2] = "movie_title"
colnames(box_office_year)[3] = "studio"
colnames(box_office_year)[4] = "total_gross"
colnames(box_office_year)[5] = "theaters"
colnames(box_office_year)[6] = "opening"
colnames(box_office_year)[7] = "theaters_opening"  

box_office_year = box_office_year %>% 
  dplyr::select(movie_title, studio, total_gross, opening) %>% 
  .[3:102,] %>%
  mutate(year = 2005 + i)
    
boxoffice = bind_rows(boxoffice, box_office_year)  
}
```

```{r combine and tidy dataset, echo=FALSE, warning=FALSE}
set.seed(1)
# renmae the movie_title in movie dataset in order to join two datasets
movie_rename = movie %>% 
  clean_names() %>% 
  rename("movie_title" = "title",
         "review_score" = "metascore")

# joining two datasets; tidy data set
movie_with_boxoffice = left_join(movie_rename, boxoffice, by=c("movie_title", "year")) %>% 
  rename("open_gross" = "opening")  

# Replace NA values in total_gross with the revenue column in movie dataset
total_gross_na = is.na(movie_with_boxoffice$total_gross)

movie_with_boxoffice$total_gross[total_gross_na] =  movie_with_boxoffice$revenue_millions[total_gross_na]*10^6

# eliminate $sign and "," of the total gross and open gross, remove rows with review scores is NA:
movie_with_boxoffice = movie_with_boxoffice %>% 
  mutate(total_gross = gsub("\\$", "", total_gross),
         total_gross = gsub(",", "", total_gross),
         total_gross = as.numeric(total_gross),
         open_gross = gsub("\\$", "", open_gross),
         open_gross = gsub(",", "", open_gross),
         open_gross = as.numeric(open_gross)) %>% 
  mutate(total_gross_millions = total_gross / 10^6,
         open_gross_millions = open_gross / 10^6,
         actors_sep = actors) %>% 
  dplyr::select(-total_gross, -revenue_millions, -open_gross) %>% 
  separate(., actors_sep, c("actor1","actor2", "actor3", "actor4"), sep=",")


```

#develop relationship between open_gross and other possible indicators

```{r the top 10 highest open-gross movie, echo=FALSE, warning=FALSE}

movie_with_boxoffice %>%
  arrange(desc(open_gross_millions)) %>% 
  dplyr::select(-description) %>% 
  head(10) %>% 
  datatable()
```
From the table above, we can see the top 10 movies with the 10 best opening gross, with highest the Jurassic World about 209 millions. Interestingly, the top 2 movies with best opening gross both released in the year 2015. The following 2 are released in the year 2016. The director Nolan has two movies with best 10 opening gross, both are batman. These gave me sense that 6 movies in the top 10 are superhero movies, 2 are hunger game series, 1 is Pirates of the Caribbean series. Therefore, it seems that the movies with highest opening gross are those popcorn series movies.

##Is there a relationship between open gross and review score?

```{r, echo=FALSE, warning=FALSE}
# visualize the linear regression 
movie_with_boxoffice %>% 
  na.omit() %>% 
  ggplot(aes(x= review_score, y = open_gross_millions)) +
  geom_point(alpha = .5) +
  stat_smooth(method = "lm") 

movie_with_boxoffice %>% 
  na.omit() %>% 
  group_by(year) %>% 
  ggplot(aes(x= review_score, y = open_gross_millions)) +
  geom_point(alpha = .5) +
  stat_smooth(method = "lm")+
  facet_grid(. ~ year)+
  theme(axis.text.x = element_text(angle = 90))

```
From the scatterplots given above, we may consider that, there seems not be very strong linear association between review score and opening gross millions through the scope of 2006-2016 years. What's more, if we seperate the review scores by years, the year 2006, 2007, 2011, the plots seems to give out negative association between review_score and opening gross. However, the year 2008 ,2012, 2014 ,2015, the association between review score and opening gross seems to be possitive.


```{r, echo=FALSE, warning=FALSE}
set.seed(1)
#Fit a linear regression model for review score and opening gross
lm(open_gross_millions ~ review_score, data = movie_with_boxoffice) %>% 
  summary() %>% 
  broom::tidy() %>% 
  datatable()

qt(0.975, df=998)


```
From the linear regression given above, we can see that the$\beta_{1}$'s p-value is 0.28 far above 0.05, we may consider this not be a siginificant predictor. The sd of review score is 0.09 while the $t_{0.975,998}$ is 1.96, $t^{*}<t_{0.975,998}$, we fail to rejct the null, while $H_{0}$:$\beta_{1}$=0. Therefore, there seems to be no relationship between review score and open gross.

```{r the top 10 review score with its open_gross, echo=FALSE, warning=FALSE}

movie_with_boxoffice %>%
  arrange(desc(review_score)) %>% 
  dplyr::select(-description) %>% 
  head(10) %>% 
  datatable()
```
It seems that none of the top 10 review score movie appears in the top 10 opening gross movies.
So will the worst 10 review score movies contain top 10 opening gross movies?
```{r the worst 10 review score with its open_gross, echo=FALSE, warning=FALSE}

movie_with_boxoffice %>%
  arrange(review_score) %>% 
  dplyr::select(-description) %>% 
  head(10) %>% 
  datatable()
```
Luckily, the worst 10 review score don't contain the top 10 opening gross movies.


##Is there a relationship between open gross and rating?
```{r, echo=FALSE, warning=FALSE}
# visualize the linear regression 
movie_with_boxoffice %>% 
  na.omit() %>% 
  ggplot(aes(x=rating, y = open_gross_millions)) +
  geom_point(alpha = .5) +
  stat_smooth(method = "lm") 



plot_ly(movie_with_boxoffice, x = ~rating, y = ~year, z = ~open_gross_millions,
        marker = list(color = ~open_gross_millions, colorscale = c('#FFE1A1', '#683531'), showscale = TRUE)) %>%
  add_markers() %>%
  layout(scene = list(xaxis = list(title = 'Rating'),
                     yaxis = list(title = 'Year'),
                     zaxis = list(title = "Open_gross_millions")),
         annotations = list(
           x = 1.13,
           y = 1.05,
           text = 'open_gross_millions',
           xref = 'paper',
           yref = 'paper',
           showarrow = FALSE
         ))

```
From the first scatterplot, we see that the linear association between rating and open gross seems to be flat. Overall, it's a postive association. From the 3d scatterplot we can see that, there seems to be some outliers, however the distribution between rating and opening gross seems to be fairly similar through years.


```{r, echo=FALSE, warning=FALSE}

#Fit a linear regression model for review score and opening gross
opengross_rating_lm <- lm(open_gross_millions ~ rating, data = movie_with_boxoffice) 

opengross_rating_lm %>% 
  summary() %>% 
  broom::tidy() %>% 
  datatable()

qt(0.975, df=998)

```
Since the sd of rating is 1.79 < $t_{0.975, 998}$ ,therefore, we still fail to reject the null, there seems to be no linear association between rating and movie_with_boxoffcie.

```{r find the outliers, echo=FALSE, warning=FALSE}

stu_res<-rstandard(opengross_rating_lm)
outliers_y<-stu_res[abs(stu_res)>2.5]
outliers_y %>% 
  as.tibble() %>% 
  datatable()

```
There seems to be 10 outliers in y.



```{r the top 10 rating with its open_gross, echo=FALSE, warning=FALSE}

movie_with_boxoffice %>%
  arrange(desc(rating)) %>% 
  dplyr::select(-description) %>% 
  head(10) %>% 
  datatable()
```
The two sets of Dark Knites appear again, and they are both directed by Christopher Nolan. He is indeed a good director.

So will the worst 10 rating movies contain top 10 opening gross movies?
```{r the worst 10 rating with its open_gross, echo=FALSE, warning=FALSE}

movie_with_boxoffice %>%
  arrange(rating) %>% 
  dplyr::select(-description) %>% 
  head(10) %>% 
  datatable()
```
Luckily, the worst 10 rating don't contain the top 10 opening gross movies.

## Is there a relationship between open gross and genre?
```{r, echo=FALSE, warning=FALSE}
set.seed(1)

movie_with_boxoffice_genre_sep = movie_with_boxoffice %>%
  mutate(genre = as.character(genre)) %>% 
  tidytext::unnest_tokens(word, genre) %>% 
  mutate(genre = word) %>% 
  filter(!genre=="fi") %>% 
  mutate(genre = stringr::str_replace(genre, "sci", "sci-fi")) 

# check if genre is a significant predictor
anova(lm(open_gross_millions ~ genre, data = movie_with_boxoffice_genre_sep))

# fit linear regression for each genre
lm(open_gross_millions ~ genre, data = movie_with_boxoffice_genre_sep) %>% 
  summary() %>% 
  broom::tidy() %>% 
  filter(p.value < 0.05) %>% 
  datatable()

movie_with_boxoffice_genre_sep %>%   
  arrange(desc(open_gross_millions)) %>% 
  pull(genre) %>% 
  head(10)

  
movie_with_boxoffice_genre_sep %>% 
plot_ly(., x = ~genre,  y = ~open_gross_millions, color = ~genre, type = "box")


colors <- c('rgb(211,94,96)', 'rgb(128,133,133)', 'rgb(144,103,167)', 'rgb(171,104,87)', 'rgb(114,147,203)')

plot_ly(movie_with_boxoffice_genre_sep, labels = ~genre, values = ~open_gross_millions, type = 'pie',
        textposition = 'inside',
        textinfo = 'label+percent',
        insidetextfont = list(color = '#FFFFFF'),
        hoverinfo = 'text',
        text = ~paste('$', open_gross_millions, ' millions'),
        marker = list(colors = colors,
                      line = list(color = '#FFFFFF', width = 1)),
                      #The 'pull' attribute can also be used to create space between the sectors
        showlegend = FALSE) %>%
  layout(title = 'Opening gross from 2006:2016',
         xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
         yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE))
  
```

### Is there a relationship between open gross and director?

```{r, include=FALSE, warning=FALSE}
set.seed(1)

# check if director is a significant predictor
anova(lm(open_gross_millions ~ director, data = movie_with_boxoffice))
## significant

# fit linear regression for directors
lm(open_gross_millions ~ director, data = movie_with_boxoffice) %>% 
  summary() %>% 
  broom::tidy() %>% 
  filter(p.value < 0.5) %>% 
  DT::datatable() 

# visualize the relationship between total gross and 

movie_with_boxoffice %>% 
  plot_ly(x = ~director,  y = ~open_gross_millions, color = ~director, type = "box") %>% 
  layout(showlegend = FALSE)

movie_with_boxoffice %>% 
  arrange(desc(open_gross_millions)) %>% 
  pull(director) %>% 
  head(10)

```

### Is there a relationship between open gross and actor?
```{r, include=FALSE, warning=FALSE}
set.seed(1)

# separate the actors in actor column into four columns; then use gather function in order to do the anova test.
movie_with_boxoffice_actor_combi= 
  movie_with_boxoffice %>%
  gather(., key = "num_actor", value = "main_actors", actor1:actor4)

# check if genre is a significant predictor
anova(lm(open_gross_millions ~ main_actors, data = movie_with_boxoffice_actor_combi))
## not significant


# visualize the relationship between total gross and 

movie_with_boxoffice_actor_combi %>% 
  plot_ly(x = ~main_actors,  y = ~open_gross_millions, color = ~main_actors, type = "box") %>% 
  layout(showlegend = FALSE)

movie_with_boxoffice_actor_combi %>%
  group_by(main_actors) %>% 
  arrange(desc(open_gross_millions)) %>% 
  head(10) %>% 
  dplyr::select(movie_title, main_actors) %>% 
  knitr::kable()
  
```

Finally we may want to find a overall linear regression for opening gross
```{r, include=FALSE, warning=FALSE}
# fit linear regression for opening gross (use stepwise regression)
mult_fit <- lm(open_gross_millions ~ review_score + year + runtime_minutes + rating + votes, data = movie_with_boxoffice)

mult_fit %>% 
 summary() %>% 
 broom::tidy() %>% 
 datatable()


best <- function(model, ...) 
{
  subsets <- regsubsets(formula(model), model.frame(model), ...)
  subsets <- with(summary(subsets),
                  cbind(p = as.numeric(rownames(which)), which, rss, rsq, adjr2, cp, bic))
  
  return(subsets)
}  


# Select the 'best' 1 model of all subsets
round(best(mult_fit, nbest = 1), 4)

best_fit <-lm(open_gross_millions ~ year + rating + votes, data = movie_with_boxoffice)

best_fit %>% 
 summary() %>% 
 broom::tidy() %>% 
 datatable()


```
From the tables given above, we select the smallest bic value, which is model with 3 predictors with bic  -128.6889(year, rating, vote). The regression model is $open_gross = -2791.6 + 1.44 year - 13.55rating + 0.0001votes$
