---
title: "p8105_final_jh3909"

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r packages, include=FALSE}
library(dplyr)
library(tidyverse)
library(httr)
library(rvest)
library(janitor)
library(stringr)
library(ggplot2)
library(hexbin)
library(plotly)
library(knitr)
```

# Prepare datasets
```{r data_prepare, include=FALSE}
# read IMDB data from Kaggle
movie = read.csv("IMDB-Movie-Data.csv")

# read boxoffice data from internet
url_base = "http://www.boxofficemojo.com/yearly/chart/?view=releasedate&view2=domestic&yr="

# create url strings for 2006 - 2016 boxoffice data; only include movies with top 100 total gross in each year. 
urls = str_c(url_base, 2006:2016, "&sort=gross&order=DESC&p=.htm")
output = vector("list", 11)

# create for loop to generate the 2006 - 2016 boxoffice dataframe
boxoffice = NULL
for (i in 1:11) {

output[[i]] = read_html(urls[[i]])

output[[i]] %>% 
html_nodes(css = "table")

box_office_year = (output[[i]] %>% html_nodes(css = "table"))[[7]] %>%
  html_table(fill = TRUE) 
  
colnames(box_office_year) = box_office_year[1,]
colnames(box_office_year)[2] = "movie_title"
colnames(box_office_year)[3] = "studio"
colnames(box_office_year)[4] = "total_gross"
colnames(box_office_year)[5] = "theaters"
colnames(box_office_year)[6] = "opening"
colnames(box_office_year)[7] = "theaters_opening"  

box_office_year = box_office_year %>% 
  select(movie_title, studio, total_gross, opening) %>% 
  .[3:102,] %>%
  mutate(year = 2005 + i)
    
boxoffice = bind_rows(boxoffice, box_office_year)  
}
```

```{r combine and tidy dataset}
set.seed(1)
# renmae the movie_title in movie dataset in order to join two datasets
movie_rename= movie %>% 
  clean_names() %>% 
  rename("movie_title" = "title",
         "review_score" = "metascore")

# joining two datasets; tidy data set
movie_with_boxoffice = left_join(movie_rename, boxoffice, by=c("movie_title", "year")) %>% 
  rename("open_gross" = "opening")  

# Replace NA values in total_gross with the revenue column in movie dataset
total_gross_na = is.na(movie_with_boxoffice$total_gross)

movie_with_boxoffice$total_gross[total_gross_na] =  movie_with_boxoffice$revenue_millions[total_gross_na]*10^6

# eliminate $sign and "," of the total gross and open gross, remove rows with review scores is NA:
movie_with_boxoffice = movie_with_boxoffice %>% 
  mutate(total_gross = gsub("\\$", "", total_gross),
         total_gross = gsub(",", "", total_gross),
         total_gross = as.numeric(total_gross),
         open_gross = gsub("\\$", "", open_gross),
         open_gross = gsub(",", "", open_gross),
         open_gross = as.numeric(open_gross)) %>% 
  mutate(total_gross_millions = total_gross / 10^6,
         open_gross_millions = open_gross / 10^6,
         actors_sep = actors,
         genre_sep = genre) %>% 
  select(-total_gross, -revenue_millions, -open_gross) %>% 
  separate(., actors_sep, c("actor1","actor2", "actor3", "actor4"), sep=",") %>% 
  separate(genre_sep, into = c("genre1", "genre2", "genre3"), sep = ",")


```

----------------------------------------------------------------------------------------------------------------------------

# Jingxuan' s code:
  
## For review scores, can box office/genre/actor/director be indicators?
  
### Can box office be the indicator of review scores?
```{r}
set.seed(1)

movie_with_review_narm = 
  movie_with_boxoffice %>% 
  filter(!is.na(review_score)) 

# fit linear regression for review scoreand total gross
lm(review_score ~ total_gross_millions , data = movie_with_review_narm) %>% 
  summary() 
### significant

movie_with_review_narm %>% 
  ggplot(aes(x= total_gross_millions, y = review_score)) +
  geom_point(alpha = .5) +
  stat_smooth(method = "lm") 
```

**Comment:**

* We can see that the positive association between review scores and boxoffice is significant. With every million increase in boxoffice, the expected review score will increase by 0.023 on average.


### Can genere be the indicator of review scores?
```{r}
set.seed(1)

# check if genre is a significant predictor
anova(lm(review_score ~ genre, data = movie_with_review_narm))
### significant

# fit linear regression for significant genre predictor
movie_with_review_narm %>%
  mutate(genre = as.character(genre)) %>% 
  tidytext::unnest_tokens(word, genre) %>% 
  mutate(genre = word) %>% 
  filter(!genre=="fi") %>% 
  mutate(genre = stringr::str_replace(genre, "sci", "sci-fi")) %>%
  lm(review_score ~ genre, .) %>% 
  broom::tidy() %>%
  filter(p.value < 0.05) %>%
  arrange(desc(estimate))

# visualize the relationship between total gross and 

movie_with_review_narm %>%
  mutate(genre = as.character(genre)) %>% 
  tidytext::unnest_tokens(word, genre) %>% 
  mutate(genre = word) %>% 
  filter(!genre=="fi") %>% 
  mutate(genre = stringr::str_replace(genre, "sci", "sci-fi")) %>% 
  plot_ly(., x = ~genre,  y = ~review_score, color = ~genre, type = "box")
```


### Can director be the indicator of review scores?
```{r}
set.seed(1)

# check if director is a significant predictor
anova(lm(review_score ~ director, data = movie_with_review_narm))
## significant

# fit linear regression for significant director predictor
lm(review_score ~ director, data = movie_with_review_narm) %>% 
  broom::tidy() %>%
  filter(p.value < 0.05) %>%
  arrange(desc(estimate))

# visualize the relationship between total gross and 

movie_with_review_narm %>% 
  plot_ly(x = ~director,  y = ~review_score, color = ~director, type = "box") %>% 
  layout(showlegend = FALSE)
```

**Fun Finding! :**

### Can actor be the indicator of review scores?
```{r}
set.seed(1)

# separate the actors in actor column into four columns; then use gather function in order to do the anova test.
review_score_actor_sep= 
  movie_with_review_narm %>%
  gather(., key = "num_actor", value = "main_actors", actor1:actor4)

# check if actor is a significant predictor
anova(lm(review_score ~ main_actors, data = review_score_actor_sep))
## significant

# fit linear regression for significant director predictor
lm(review_score ~ main_actors, data = review_score_actor_sep) %>% 
  broom::tidy() %>%
  filter(p.value < 0.05) %>%
  arrange(desc(estimate))

# visualize the relationship between total gross and 

review_score_actor_sep %>% 
  plot_ly(x = ~main_actors,  y = ~review_score, color = ~main_actors, type = "box") %>% 
  layout(showlegend = FALSE)
```

### Can studio be the indicator of review scores?
```{r}
set.seed(1)

# check if studio is a significant predictor
anova(lm(review_score ~ studio, data = movie_with_review_narm))
### significant

# fit linear regression for significant genre predictor
lm(review_score ~ studio, data = movie_with_review_narm) %>% 
  broom::tidy() 

# visualize the relationship between total gross and 

movie_with_review_narm %>% 
  plot_ly(., x = ~genre,  y = ~review_score, color = ~studio, type = "box")
```