---
title: "P8105_final_mc4433"
author: "Manqi Cai"
date: "11/28/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#The relationship between gross at the opening week and total gross?
#The relationship between  gross at the opening week and director?

```{r packages}
library(dplyr)
library(tidyverse)
library(httr)
library(rvest)
library(janitor)
library(stringr)
```

```{r data_prepare, include=FALSE}
movie = read.csv("IMDB-Movie-Data.csv")

boxoffice = NULL

url_base = "http://www.boxofficemojo.com/yearly/chart/?view=releasedate&view2=domestic&yr="
urls = str_c(url_base, 2006 : 2016, "&sort=gross&order=DESC&p=.htm")

output = vector("list", 11)

for (i in 1:11) {

output[[i]] = read_html(urls[[1]])

output[[i]] %>% 
html_nodes(css = "table")

box_office_year = (output[[i]] %>% html_nodes(css = "table"))[[7]] %>%
  html_table(fill = TRUE) 
  
colnames(box_office_year) = box_office_year[1,]
colnames(box_office_year)[2] = "movie_title"
colnames(box_office_year)[3] = "studio"
colnames(box_office_year)[4] = "total_gross"
colnames(box_office_year)[5] = "theaters"
colnames(box_office_year)[6] = "opening"
colnames(box_office_year)[7] = "theaters_opening"  

box_office_year = box_office_year %>% 
  select(movie_title, studio, total_gross, opening) %>% 
  .[3:102,] %>%
  mutate(year = 2005 + i)
    
boxoffice = bind_rows(boxoffice, box_office_year)  
}


```

```{r}
set.seed(1)
# renmae the movie_title in movie dataset in order to join two datasets
movie_rename= movie %>% 
  clean_names() %>% 
  rename("movie_title" = "title",
         "review_score" = "metascore")

# joining two datasets; tidy data set
movie_with_boxoffice = left_join(movie_rename, boxoffice, by=c("movie_title", "year")) %>% 
  rename("open_gross" = "opening") %>% 
  filter(!is.na(total_gross) | !is.na(revenue_millions) | !is.na(open_gross))  %>% 
  mutate(total_gross = gsub("\\$", "", total_gross),
         total_gross = as.numeric(total_gross),
         open_gross = gsub("\\$", "", open_gross),
         total_gross = as.numeric(open_gross))



 
