
---
title: "Movie explore"
runtime: shiny
output: 
  flexdashboard::flex_dashboard:
    theme: cosmo
    orientation: columns
    vertical_layout: fill
    source_code: embed
---
```{r global, include=FALSE}
library(readr)
library(tidyverse)
library(janitor)
library(stringr)
library(forcats)
library(viridis)
library(plotly)
library(shiny)
library(flexdashboard)
library(httr)
library(rvest)
library(viridis)
```

```{r data_prepare, warning=FALSE}
# read IMDB data from Kaggle
movie = read.csv("./data/IMDB-Movie-Data.csv")

# read boxoffice data from internet
url_base = "http://www.boxofficemojo.com/yearly/chart/?view=releasedate&view2=domestic&yr="

# create url strings for 2006 - 2016 boxoffice data; only include movies with top 100 total gross in each year. 
urls = str_c(url_base, 2006:2016, "&sort=gross&order=DESC&p=.htm")
output = vector("list", 11)

# create for loop to generate the 2006 - 2016 boxoffice dataframe
boxoffice = NULL
for (i in 1:11) {

output[[i]] = read_html(urls[[i]])

output[[i]] %>% 
html_nodes(css = "table")

box_office_year = (output[[i]] %>% html_nodes(css = "table"))[[7]] %>%
  html_table(fill = TRUE) 
  
colnames(box_office_year) = box_office_year[1,]
colnames(box_office_year)[2] = "movie_title"
colnames(box_office_year)[3] = "studio"
colnames(box_office_year)[4] = "total_gross"
colnames(box_office_year)[5] = "theaters"
colnames(box_office_year)[6] = "opening"
colnames(box_office_year)[7] = "theaters_opening"  

box_office_year = box_office_year %>% 
  dplyr::select(movie_title, studio, total_gross, opening) %>% 
  .[3:102,] %>%
  mutate(year = 2005 + i)
    
boxoffice = bind_rows(boxoffice, box_office_year)  
}

set.seed(1)
# renmae the movie_title in movie dataset in order to join two datasets
movie_rename= movie %>% 
  clean_names() %>% 
  rename("movie_title" = "title",
         "review_score" = "metascore")

# joining two datasets; tidy data set
movie_with_boxoffice = left_join(movie_rename, boxoffice, by=c("movie_title", "year")) %>% 
  rename("open_gross" = "opening")  

# Replace NA values in total_gross with the revenue column in movie dataset
total_gross_na = is.na(movie_with_boxoffice$total_gross)

movie_with_boxoffice$total_gross[total_gross_na] =  movie_with_boxoffice$revenue_millions[total_gross_na]*10^6

# eliminate $sign and "," of the total gross and open gross, remove rows with review scores is NA:
movie_with_boxoffice = movie_with_boxoffice %>% 
  mutate(total_gross = gsub("\\$", "", total_gross),
         total_gross = gsub(",", "", total_gross),
         total_gross = as.numeric(total_gross),
         open_gross = gsub("\\$", "", open_gross),
         open_gross = gsub(",", "", open_gross),
         open_gross = as.numeric(open_gross)) %>% 
  mutate(total_gross_millions = total_gross / 10^6,
         open_gross_millions = open_gross / 10^6,
         actors_sep = actors,
         genre_sep = genre) %>% 
  select(-total_gross, -revenue_millions, -open_gross) %>% 
  separate(., actors_sep, c("actor1","actor2", "actor3", "actor4"), sep=",") %>% 
  separate(genre_sep, into = c("genre1", "genre2", "genre3"), sep = ",")
```



Column {.sidebar}
-----------------------------------------------------------------------
 
```{r}

# selectInput widget-boro
year = movie_with_boxoffice %>% distinct(year) %>% pull()
checkboxGroupInput("year", label = h3("Select year for bar plot"),
            choices = year, selected = c("2016","2015","2014"))







```


Row
-----------------------------------------------------------------------

### line plot

```{r}
##plot that shows number of row for each grade date
renderPlotly({
  movie_with_boxoffice %>%
  group_by(year) %>% 
  mutate(box_office_year = sum(total_gross_millions, na.rm = TRUE)) %>% 
  ungroup() %>% 
  filter(year == input$year) %>% 
  plot_ly(x = ~year, y = ~box_office_year, type = 'bar' ,
mode = 'markers' ) %>% 
  layout(margin = list(b = 160))

})
```


Row
-----------------------------------------------------------------------

### line plot

```{r}
##plot that shows number of row for each grade date
renderPlotly({
  movie_with_boxoffice %>%
  group_by(year) %>% 
  mutate(open_box_office_year = sum(open_gross_millions, na.rm = TRUE)) %>% 
  ungroup() %>% 
  filter(year == input$year) %>% 
  plot_ly(x = ~year, y = ~open_box_office_year, type = 'bar' ,
mode = 'markers' ) %>% 
  layout(margin = list(b = 160))

})
```

Row
-----------------------------------------------------------------------

### line plot

```{r}
##plot that shows number of row for each grade date
renderPlotly({
  movie_with_boxoffice %>%
  group_by(year) %>% 
  mutate(mean_review_year = mean(review_score, na.rm = TRUE)) %>% 
  ungroup() %>% 
  filter(year == input$year) %>% 
  plot_ly(x = ~year, y = ~mean_review_year, type = 'bar' ,
mode = 'markers' ) %>% 
  layout(margin = list(b = 160))

})
```

Row
-----------------------------------------------------------------------

### line plot

```{r}
##plot that shows number of row for each grade date
renderPlotly({
  movie_with_boxoffice %>%
  group_by(year) %>% 
  mutate(mean_rating_year = mean(rating, na.rm = TRUE)) %>% 
  ungroup() %>% 
  filter(year == input$year) %>% 
  plot_ly(x = ~year, y = ~mean_rating_year, type = 'bar' ,
mode = 'markers' ) %>% 
  layout(margin = list(b = 160))

})

```

Row
-----------------------------------------------------------------------

From the four bar plots above, we can see that there is a increasing trend of total movie box office and total movie open box office from 2006 to 2016, indicating more and more people are willing to go to theater and watch movie. However, the mean review score and the mean rating of movies decreased from 2006 to 2016, indicating that even though the box office of moive is getting better, the overall quality and reputation of moives doesn't catch up. 